---
title: "Reproducible Research Project 1"
author: "JuanSe"
date: "8/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

First Step: Upload data

```{r}
data <- read.csv("activity.csv")
head(data)
data1 <-aggregate(data$steps, list(data$date), FUN=sum)
colnames(data1) <- c("date", "steps")
head(data1)
```

Now, this is a histogram of the steps taken every day

```{r}
hist(data1$steps)
```

Then, we compute the mean and median of steps taken

```{r}
mean(data1$steps, na.rm = TRUE)
median(data1$steps, na.rm = TRUE)
```

Time Series plot of the average steps taken

```{r}
data2 <-aggregate(data$steps, list(data$date), FUN=mean)
colnames(data2) <- c("date", "steps")
head(data2)
plot(data1$steps,type = 'l')
```

The inverval that has the highest average of steps

```{r}
data3 <-aggregate(steps~interval,data = data, FUN=mean)
colnames(data3) <- c("interval", "steps")
head(data3)
plot(data3$steps,type = 'l')
data3[which.max(data3$steps),]
```

Strategy for imputing missing data and histogram  
For me missing data refers to 0 steps at that interval

```{r}
data[is.na(data$steps),1] <- 0
data1 <-aggregate(data$steps, list(data$date), FUN=sum)
colnames(data1) <- c("date", "steps")
hist(data1$steps)
mean(data1$steps, na.rm = TRUE)
median(data1$steps, na.rm = TRUE)
```

Panel board for weekends and weekdays

```{r}
data$date <- as.Date(data$date, format = "%Y-%m-%d")
data$weekday <- weekdays(data$date)
data$day <- ifelse(data$weekday=='Saturday' | data$weekday=='Sunday', 'weekend','weekday')
head(data)

library(ggplot2)
data4 <- aggregate(steps~interval+day,data=data,FUN=mean)
head(data4)
g <- ggplot(data4, aes(interval, steps))
g+geom_line(col="darkblue")+ggtitle("Average steps weekdays vs weekends")+xlab("Interval")+ylab("Steps")+facet_grid(day ~ .)
```





